### 2015-03-28 Kokkos_PG_MachineModel.tex
Adds a bibliography to the reference guide and a citation to the CAL-AMM document from Sandia National Laboratories.

\begin{figure}
\includegraphics[width=2in]{figures/kokkos-node.pdf}
\caption{Conceptual Model of a Future High Performance Computing Node}
\label{fig:kokkosnode}
\end{figure}

Kokkos assumes an {\em abstract machine model} for the design of
future shared-memory computing architectures. The model (shown in
Figure~\ref{fig:kokkosnode}) assumes that there may be multiple
execution units in a compute node. In the Figure we have elected to
show two different types of compute units -- one which represents
multiple latency-optimized cores, similar to contemporary processor
cores, and a second source of compute in the form of an off die
accelerator. Of note is that the processor and accelerator each 
have distinct memories, each with unique performance properties,
that are accessible across the node ({\em i.e.} the memory is
reachable or {\em shared} by all execution units. The specific
layout shown in Figure~\ref{fig:kokkosnode} is an instantiation
of the Kokkos abstract machine model used to describe the potential
for multiple types of compute engines and memories within a single
node. In future systems there may be a range of execution engines
which are used in the node ranging from a single type of core
as in many/multi-core processors found today through to an range
of execution units where many-core processors may be joined to
numerous types of accelerator cores. In order to ensure portability
to the potential range of nodes an abstraction of the
compute engines and available memories are required.

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=4in]{figures/kokkos-node.pdf}
\caption{Conceptual Model of a Future High Performance Computing Node}
\label{fig:kokkosnode}
\end{center}
\end{figure}

Kokkos assumes an {\em abstract machine model} for the design of
future shared-memory computing architectures. The model (shown in
Figure~\ref{fig:kokkosnode}) assumes that there may be multiple
execution units in a compute node. For a more general discussion
of abstract machine models for Exascale computing the reader should
consult reference~\cite{cal_amm}. In the figure shown here,
we have elected to
show two different types of compute units -- one which represents
multiple latency-optimized cores, similar to contemporary processor
cores, and a second source of compute in the form of an off die
accelerator. Of note is that the processor and accelerator each 
have distinct memories, each with unique performance properties,
that are accessible across the node ({\em i.e.} the memory is
reachable or {\em shared} by all execution units. The specific
layout shown in Figure~\ref{fig:kokkosnode} is an instantiation
of the Kokkos abstract machine model used to describe the potential
for multiple types of compute engines and memories within a single
node. In future systems there may be a range of execution engines
which are used in the node ranging from a single type of core
as in many/multi-core processors found today through to an range
of execution units where many-core processors may be joined to
numerous types of accelerator cores. In order to ensure portability
to the potential range of nodes an abstraction of the
compute engines and available memories are required.
